Mysterious radio flashes could trace Universe's largest structures

### 2015-08-19 writeup/summary_krs.tex
New summary text for vKris

\title{Mysterious radio flashes could be used to trace Universe's largest
structures}

@@

One of the most challenging aspects of astronomy is determining distances to
far-off objects. Newly discovered fast radio bursts---thought to originate from
the far reaches of the Universe---provide distance measurements that may
enable the largest structures of the cosmos to be studied in three dimensions.
Traditionally cosmological distances are obtained using Doppler, caused
by the Hubble expansion of the Universe. In contrast, delays to fast radio
burst signals can be used to measure the total amount material between earth
and the burst's source, permitting another way to determine distance.  However
this process isn't perfect, as intervening clumps of excess matter can distort the
measured distance. This fact can be exploited to glean yet more
information through these intervening structures.  Wide-field radio telescopes
are expecting to detect thousands of these bursts, opening a new window for
studying the cosmos.

>>>>

\title{Mysterious radio flashes could trace Universe's largest structures}

@@

One fundamental aspect of astronomy is mapping the distances to far-off objects.  Newly discovered fast radio bursts---thought to originate from the far reaches of the cosmos---signal distance measurements that may enable the largest structures in the Universe to be studied in three dimensions.  Cosmological distances are traditionally determined using the redshift of photons induced by the expansion of the Universe.    In contrast, delays to fast radio bursts at different wavelengths tally the total amount of material between the burst and Earth, enabling a new  way to infer cosmological distance.  As cosmic matter distorts the inferred distances in a direction dependent way these dispersion distances don’t exactly match actual distances. However, these distortions reveal even more information about the intervening structure.  Wide-field radio telescopes could detect thousands of these bursts, opening a new window for studying the cosmos.
